Figures

### 2018-04-19 scripts/analysis.Rmd
add more exploratory plots
adjust fig caption

```{r fig.cap="Connectivity metric box", echo=FALSE}
knitr::include_graphics("../figures/conny_metric_key_crop.pdf")
```

@@

```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3.5, fig.cap="Exploratory plots cont"}

>>>>

```{r fig.cap="Definition of connectivity metrics.", echo=FALSE}
knitr::include_graphics("../figures/conny_metric_key_crop.pdf")
```

@@

```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont"}
